\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Fix grammar and probable intent
Fix grammar
Comment out half sentence; I don't know what that means

For a variety of reasons, most software development projects for open stateful protocols end up with an equilibrum where the development process is organized around a canonical collaborative state. By collaborative state we mean some sort of code base and social collaboration metadata about that code base. For example, the state may often be a Git repository, and the collaboration metadata may be repository hosting service of some kind, or it could be a curated mailing list of patches and discussion. Ultimately, some social consensus process emerges for how changes to this state is made, and almost invariably, this process becomes a source of market power, its integrity becomes a security risk, and it is not formally accountable to protocol stakeholders. Socially desirable changes may be rejected, or adopted too slowly, and changes which are undesirable may be adopted. While fork based exit is in principle an option. This results in the following specific requirements.

@@

The project itself goes through the following states after being submitted, in a normal

@@

Important to not hold on to data, if leaked, the signatures which validate the authenticity of the data include

>>>>

For a variety of reasons, most software development projects for open stateful protocols end up with an equilibrum where the development process is organized around a canonical collaborative state. By collaborative state we mean some sort of code base and social collaboration metadata about that code base. For example, the state may often be a Git repository, and the collaboration metadata may be repository hosting service of some kind, or it could be a curated mailing list of patches and discussion. Ultimately, some social consensus process emerges for how changes to this state is made, and almost invariably, this process becomes a source of market power, its integrity becomes a security risk, and it is not formally accountable to protocol stakeholders. Socially desirable changes may be rejected, or adopted too slowly, and changes which are undesirable may be adopted. While fork based exit is in principle an option, it is also costly. This results in the following specific requirements.

@@

The project itself goes through the following states after being submitted:

@@

% FIXME Important to not hold on to data, if leaked, the signatures which validate the authenticity of the data include
